An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-07-29 Article/EconGrowth2-GraphsOnly.Rnw
Changed Econ2011 to Calvin2011 everywhere in our code.
Econ2011 (Calvin2011) and Warr2000 are gone. We are how using an AllHistData object that has both.
Papers now use Calvin data frame from the EconData package.
Articles now use the new results structure.

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
historicalData <- Econ2011 # From the EconData package

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)

# Load the original models.
oModels <- OrigModels

@@

<<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
data <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
@

>>>>

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
historicalData <- Calvin # From the EconData package

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(Calvin_Coeffs)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(Calvin_Fitted)

# Load the original models.
oModels <- Calvin_Models

@@

<<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
data <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
@
